Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-17 ms.tex
Uncommenting windheat appendix and then. Few more citations.

\author[Generozov, Stone, \& Metzger]{Aleksey S. Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

@@

%\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
%\label{app:windheat}
%\input{windheat}

>>>>

\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astropysics Labratory, Columbia University, 550 West 120th Street, New York, NY 10027}

@@

\section{Analytic model for dependence of wind heating $\vwO^{\star}$ on stellar age}
\label{app:windheat}
\input{windheat}
